### 2016-07-25 report/paper_draft.tex
added tensorflow notes. added Tensorfow section.

>>>>

\subsection{Tensorflow}
Tensorflow was released by Google Research for open source in November 2015, and updated to include distributed support in 2016. The user-facing APIs are C++ and Python. Programming with Tensorflow leans more imperative than with some of the other frameworks discussed. While plenty of abstraction power is expressed in its library, the user will probably also be working with computational wrappers of primitives such as matrix operations, element-wise math operators, and looping control. In other words, the user is exposed to some of the internal workings of deep learning networks. Tensorflow sees constructed networks as a directed graph of nodes encapsulating dataflow computation and required dependencies \cite{DBLP:journals/corr/AbadiABBCCCDDDG16}. Each node, or computation, gets mapped to devices (CPUs or GPUs) according to some cost function. This partitions the overall graph into subgraphs, one per device. Cross-device edges are replaced to encode necessary synchronization between device pairs. Distributed execution appears to be a natural extension of this arrangement, except that TCP or Remote Direct Memory Access (RDMA) is used for inter-device communication on separate machines. This approach of mapping subgraphs onto devices also offers scalability potential, as each worker can schedule its own subgraph at runtime instead of relying on a centralized master \cite{DBLP:journals/corr/AbadiABBCCCDDDG16}. Parallelism in Tensorflow can be expressed at several levels, notable both data parallelism and model parallelism. Data parallelism can happen both across and within workers, by training separate batches of data on model replications. Model parallelism is expressed through splitting one model, or its graph, across devices. Model updates can either be synchronous or asynchronous for parameter-optimizing algorithms such as stochastic gradient descent (SGD). For fault tolerance, Tensorflow provides checkpointing and recovery of data designated to be persistent, while the overall computation graph is restarted. In terms of other features, TensorBoard is a tool for interactive visualization of a user's network, and also provides time series data on various aspects of the learning network's state during training.
